\LARGE{{\bf{Piled up gravitational waves:} \\ \bf{Searching for new signals of $N$naturalness} }}

### 2019-08-02 gwnnDraft02.tex
Updated phrasing and grammar

Within the framework of SM-like sectors (save the higgs mass parameter), our exotic sectors feature at most 106.75 effective degrees of freedom at high energies: 72 from quarks,  12 from charged leptons, 6 from neutrinos, 16 from gluons, 2 from photons, 6 from W bosons (no longitudinal modes due to a no symmetry breaking), 4 from the higgs sector (again, no symmetry breaking leads to 3 additional modes), for a total of 118 degress of freedom. Scaling the fermionic contributions by $7/8$ gives us 106.75 effective relativistic degrees of freedom.  After the higgses freeze out, 4 degrees of freedom are lost; when the QCD phase transition occurs 35 bosonic degrees of freedom are gained while 72 fermionic are lost, leaving 56.75 effective degrees of freedom. Since all additional sectors are colder than our own by the time photon decoupling occurs ($\sim 0.39 \,\ev$), the pions of all of these sectors have a much higher mass in accordance with Eq. (\ref{eqn:gmor}) and thus will have frozen out long before --- leaving at most $11.25$ effective degrees of freedom per sector.

Coupling the number of effective degrees of freedom per sector with the energy density scaling of $\sim 1/m_H^4$ found in the zero vev sectors leads to tiny temperature ratios. Assuming a reheating temperature of $100$ GeV and a completely uniform distribution of sectors, the temperature of the first exotic sector is slightly more than $6\%$ of our sector at reheating. Applying Eq. (\ref{eqn:DeltaNeff}) to this particular situation gives us:
\begin{equation}
\Delta N_{eff} = \sum_i \frac{4}{7}\left(\frac{11}{4}\right)^{4/3}g_{i} \left(\frac{0.06}{i^2}\right)^4.
\end{equation}     
Summing over all sectors (sectors above $i \sim 10$ essentially don't contribute due to the small temperature ratio) gives us a contribution of $\mathcal{O} (10^{-4})$. Evolving the sectors thermal histories forward in time to the recombination era gives us a slightly larger value, but still of order $\mathcal{O}(10^{-4})$; well under current CMB bounds.

>>>>

Within the framework of SM-like particle content (save the higgs mass parameter), our exotic sectors feature at most 106.75 effective degrees of freedom at high energies: 72 from quarks,  12 from charged leptons, 6 from neutrinos, 16 from gluons, 2 from photons, 6 from W bosons (no longitudinal modes due to a no symmetry breaking), 4 from the higgs sector (again, no symmetry breaking leads to 3 additional modes), for a total of 118 degress of freedom. Scaling the fermionic contributions by $7/8$ gives us 106.75 effective relativistic degrees of freedom.  After the higgses freeze out, 4 degrees of freedom are lost; when the QCD phase transition occurs 35 bosonic degrees of freedom are gained while 72 fermionic are lost, leaving 56.75 effective degrees of freedom. Since all additional sectors are colder than our own by the time photon decoupling occurs ($\sim 0.39 \,\ev$), the pions of all of these sectors will, in accordance with Eq. (\ref{eqn:gmor}), have a much higher mass than the sector temperature and thus will have frozen out long before --- leaving at most $11.25$ effective degrees of freedom per sector.

Coupling the number of effective degrees of freedom per sector with the energy density scaling of $\sim 1/m_H^4$ found in the zero vev sectors leads to tiny temperature ratios. Assuming a reheating temperature of $100$ GeV and a completely uniform distribution of sectors, the temperature of the first exotic sector is slightly more than $6\%$ of our sector at reheating. Applying Eq. (\ref{eqn:DeltaNeff}) to this particular situation gives us:
\begin{equation}
\Delta N_{eff} = \sum_i \frac{4}{7}\left(\frac{11}{4}\right)^{4/3}g_{i} \left(\frac{0.06}{i^2}\right)^4.
\end{equation}     
Summing over all sectors (sectors above $i \sim 10$ essentially don't contribute due to the small temperature ratios) gives us a contribution of $\mathcal{O} (10^{-4})$. Evolving the sectors thermal histories forward in time to the recombination era gives us a slightly larger value, but still of order $\mathcal{O}(10^{-4})$; well under current CMB bounds.
